Accelerating Taxonomic Classification of DNA Sequences Using Artificial Neural Networks

### 2025-03-17 article/main.tex
article: add temporary title, add keywords, translate missing part, add backmatter section

\documentclass[pdflatex,referee,lineno,sn-vancouver-num]{sn-jnl}% Math and Physical Sciences Numbered Reference Style

@@

    \title[Article Title]{Article Title}

@@

    \keywords{Key1, Key2, Key3}

@@

                \paragraph{Dataset}
                Zbiór danych uczących oraz walidacyjnych został stworzony na podstawie pierwszej próbki sekwencji genetycznych ze zbioru \textit{CAMI II Toy Human Microbiome Project}\cite{Fritz:2019}. Próbka zawiera symulowane dane metagenomiczne z mikrobiomu skóry człowieka. Przykłady zostały uzyskane poprzez losowanie kotwic ze zbioru oraz modyfikację tych kotwic w celu stworzenia sekwencji pozytywnej i negatywnej. Modyfikacja polegała na zamianie punktowej danego nukleotydu na inny. W przypadku sekwencji pozytywnej zmiana obejmowała od $0\%$ do $20\%$ długości kotwicy, natomiast w przypadku sekwencji negatywnej od $20\%$ do $80\%$ długości kotwicy.

@@

>>>>

\documentclass[pdflatex,sn-vancouver-num]{sn-jnl}% Math and Physical Sciences Numbered Reference Style

@@

    \title[Article Title]{Accelerating Taxonomic Classification of DNA Sequences Using Artificial Neural Networks}

@@

    \keywords{DNA sequencing, taxonomic classification, artificial neural networks, contrastive learning, sequence clustering}

@@

                \paragraph{Dataset}
                The training and validation datasets were created based on the first sample of genetic sequences from the CAMI II Toy Human Microbiome Project dataset \cite{Fritz:2019}. The sample contains simulated metagenomic data from the human skin microbiome. Examples were obtained by randomly selecting anchors from the dataset and modifying these anchors to create positive and negative sequences. The modification involved a point mutation of a given nucleotide to another one. In the case of positive sequences, the change affected between 0\% and 20\% of the anchor length, whereas for negative sequences, the change ranged from 20\% to 80\% of the anchor length.

@@

    %%=============================================================%%
    %% BACKMATTER
    %%=============================================================%%

    \backmatter
